Comparative study of Dask and Spark for neuroimaging pipelines\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Natural Sciences and Engineering Research Council}

### 2019-06-14 latex/paper.tex
Modified the engines section

\subsubsection{Dask Bag~\cite{dask-bag}} Dask Bag is one of the high-level API
offered by dask. It also provides in-memory computing, data locality and lazy
evaluation however it does not have fault resilience. Fundamently it is parallized
lists. Dask Bag parallelizes computations of large collection of generic python
objects~\cite{dask-bag}. Also, it offers optimized algorithm that mimic most the
toolz library. Our experiment use the dask distributed~\cite{dask-distributed}
scheduler. It has a LIFO policy. In theory it should speed-up the computation by
finishing task computations before starting new ones.

\subsubsection{Dask Delayed~\cite{dask-delayed}} Dask Delayed is a low-level API. It
does not offer the optimized algorithm as the high-level APIs however it allows the
user to parallelize custom function that do not fit in the array, dataframe or
MapReduce framework.

\subsubsection{Dask Futures~\cite{dask-futures}} Dask Futures is also a low-level API
from dask. It differs from the other APIs as its computations trigger immediately.

>>>>

\subsubsection{Dask Bag~\cite{dask-bag}} Dask Bag is one of the high-level API
offered by dask. Like Spark, it provides in-memory computing, data locality and lazy
evaluation however it does not have fault resilience. Fundamently it is parallized
lists. Dask Bag parallelizes computations of large collection of generic python
objects~\cite{dask-bag}. Also, it offers optimized algorithm that mimic most of the
toolz library. Our experiment use the Dask Distributed~\cite{dask-distributed}
scheduler. It has a LIFO policy. In theory it should speed-up the pipeline excution
by finishing task computations before starting new ones.

\subsubsection{Dask Delayed~\cite{dask-delayed}} Dask Delayed is a low-level API. It
does not offer the optimized algorithm as the high-level APIs however it allows the
user to parallelize custom function that do not fit in the array, dataframe or
MapReduce framework. This is perfect for more complex function which could easily be
parallelized. Like Dask Bag, it offers in-memory computing, data locality and lack
fault resilience. The Dask Distributed scheduler.

\subsubsection{Dask Futures~\cite{dask-futures}} Dask Futures is also a low-level API
from Dask. Like the other Dask APIs it benifit of in-memory computing and data
locatlity. Unlike the other APIs, Dask Futures triggers computation immediately. When
the user tries to gather data, if available it will return the result otherwise it
will block until the cimputation is done.
